
\begin{thebibliography}{99}

\bibitem{Ari13} O. Arizmendi. Convergence of the fourth moment and infinite divisibility 
\emph{Probab. Math. Statist.} {\bf 33} (2013), no. 2, 201--212.

\bibitem{Ari18} O. Arizmendi. $k$-divisible random variables and  
\emph{Adv. App. Math.} {\bf 93} (2018), 1--68.

\bibitem{AHLV15} O. Arizmendi, T. Hasebe, F. Lehner, C. Vargas. Relations between cumulants in non-commutative probability 
\emph{Adv. Math.} {\bf 282} (2015), 10, 56--92.

\bibitem{AV12} O. Arizmendi, C. Vargas. Products of free random variables and $k$-divisible partitions  
\emph{Electron. Commun. Probab.} {\bf 17} (2012), 11, 13 pp.

\bibitem{BS91} M. Bozejko, R. Speicher, $\psi$-simmetrized and independent white noises, \emph{Quantum probability and related topics (L. Accardi Ed.)} vol {\bf VI}, World Scientific, Singapore, 219--236, 1991.

\bibitem{BLS96} M. Bozejko, M. Leinert and R. Speicher. Convolution and limit theorems for conditionally
free random variables. \emph{Pac. J. Math.} {\bf 175}, 357--388, (1996).

\bibitem{Fra06} U. Franz. Multiplicative monotone convolutions \emph{Quantum Probability, M. Bozejko, W. Mlotkowski and J. Wysoczanski (eds.), Banach Center Publications} {\bf 73}, 153--166, (2006).

\bibitem{HS11} T. Hasebe, H.Saigo. The monotone cumulants. \emph{Ann. Inst. H. Poincaré Prob. Statist.} Vol {\bf 47}, No 4 (2011), 1160--1170.

\bibitem{Has11} T. Hasebe. Conditionally monotone independence I: Independence, additive convolutions and related convolutions. \emph{Infin. Dimens. Anal. Quantum. Probab. Relat. Top.} {\bf 14}, no. 3, 465--516, (2011).

\bibitem{Has13} T. Hasebe. Conditionally monotone independence II: Multiplicative convolutions and infinite divisibility. \emph{Complex Anal. Op. Th.} {\bf 7}, no. 1, 115--134, (2013).

\bibitem{Hud73} R. L. Hudson. A quantum mechanical central limit theorem for anticommuting observables.
\emph{J. Appl. Prob.} {\bf 10}, 502--509, (1973).

\bibitem{Kre72} G. Kreweras, Sur les partitions non-croisées d’un cycle, \emph{Discrete Mathematics} {\bf 1} (1972), 333--350.

\bibitem{Mal11} C. Male. Traffic distributions and independence: permutation invariant random matrices and the three notions of independence. Preprint, (2011).

\bibitem{MP67} V. Mar\v cenko and L. Pastur. Distribution of eigenvalues for some
sets of random matrices, \emph{Math. USSR-Sbornik} {\bf 1}, 457--483, (1967).

\bibitem{Mlo02} W. Mlotkowski, Operator-valued version of conditionally free product, \emph{Studia Mathematica} {\bf 153} no.1, 2012.
% Segundo funcional es lineal.

\bibitem{NS06} A. Nica, R. Speicher, \emph{Lectures on the combinatorics of free probability}, London Mathematical Society Lecture Note Series, vol. {\bf 335}, Cambridge University Press, Cambridge, 2006.

\bibitem{Spe94} R. Speicher. Multiplicative functions on the lattice of noncrossing partitions
and free convolution, \emph{Math. Ann.} {\bf 298}, no. 4, 611--628, (1994).

\bibitem{PVW15} M. Popa, V. Vinnikov, J.-C. Wang, On the multiplication of operator-valued C-free random variables, \emph{Colloquium Mathematicum} {\bf 153}(2), 2015.
% S.transform twisted multiplicativity, etc

\bibitem{PW11} M. Popa, J.-C. Wang, On multiplicative conditionally free convolution, \emph{Trans. Amer. Math. Soc. 363 (2011)} {\bf 363} no. 12, 6309--6335 2011.
% caso escalar

\bibitem{Pop08} M. Popa, Multilinear function series in conditionally free probability with amalgamation, \emph{Communications on Stochastic Analysis} Vol. {\bf 2}, No. 2 (2008) 307--322.
% positividad, caso inverso al que nosotros presentamos.

\bibitem{Spe98} R. Speicher. \emph{Combinatorial theory of the free product with amalgamation
and operator-valued free probability theory}. Memoirs of the American Math.
Society, vol. {\bf 132}, (1998).

\bibitem{Voi85} D. Voiculescu. Symmetries of some reduced free product $C^*$-algebras,\emph{Operator
algebras and their connections with topology and ergodic theory (Busteni,
1983), Lecture Notes in Math.}, vol. {\bf 1132}, Springer, Berlin, 556--588, (1985).

\bibitem{Voi91} D. Voiculescu. Limit laws for random matrices and free products, \emph{Invent. Math.} {\bf 104}, 201--220, (1991).

\bibitem{VDN92} D. Voiculescu, K. Dykema and A. Nica. \emph{Free Random Variables}, CRM Monograph Series, Vol. {\bf 1}, AMS, (1992).

\bibitem{Voi95} D. Voiculescu. Operations on certain non-commutative operator-valued random
variables. \emph{Recent advances in operator algebras (Orleans, 1992). Asterisque} {\bf 232}, (1995).

\bibitem{Wig58} E. Wigner. On the distribution of the roots of certain symmetric matrices, \emph{Ann. of Math.} {\bf 67}, 325--327, (1958).

\end{thebibliography}

hg
agregar Ben-G schurman y Belinschi -N- S 
SW Booolean
Bozeko solo 96?